---
title: "Interactive Graphs in R"
---

These are examples related to the _Interactive Data Visualization with Plotly_ course on [DataCamp](datacamp.com)

```{r, message=FALSE}
if (!require("dplyr")) install.packages("dplyr")
library(dplyr)
library(plotly)
library(rattle)

```
#Static Graph 1
```{r}
head(wine)
library(ggplot2)
g <- wine %>% ggplot(aes(Flavanoids, Proline, color = Type, size = Hue)) +
  geom_point()
g
```

#Interactive Graph 1
```{r}

ggplotly(g)
```

#Static Graph 2

```{r}
ggplot(wine, aes(Phenols, fill = "red")) +
  geom_bar(binwidth = 0.15)
```

#Interactive Graph 2
```{r}
wine %>%
  plot_ly(x = ~Phenols, hoverinfo = "y") %>%
  add_histogram(opacity = 0.7, color = I("pink"), nbinsx = 25)
```

#Data Wrangling
```{r}
# Data Citation:
# P. Cortez, A. Cerdeira, F. Almeida, T. Matos and J. Reis. 
# Accessed from UCI website.
# Modeling wine preferences by data mining from physicochemical properties. In Decision Support Systems, Elsevier, 47(4):547-553, 2009.
winequality <- read.csv("winequality-red.csv",header = TRUE,sep = ";")
#str(winequality)

winequality$type <- "red" 


winequality2 <- read.csv("winequality-white.csv", header = TRUE, sep = ";")
#str(winequality2)

winequality2$type <- "white"

totalwine <- rbind(winequality, winequality2)

totalwine$type <- factor(totalwine$type)

str(totalwine)

totalwine <- totalwine[c(1:11,13,12)]

totalwine$quality <- as.character(totalwine$quality)
```

#Interactive Graph Bars
```{r}
totalwine %>%
  count(type, quality) %>%
  plot_ly(x = ~type, y = ~n, color = ~quality) %>%
  add_bars() %>%
  layout(barmode = "stack")

  
```



```{r}

for (x in 1:nrow(totalwine)){
  if (totalwine$quality[x] == "9" | totalwine$quality[x] == "8" | totalwine$quality[x]== "7"){
    totalwine$quality[x] <- "High"
  }else if (totalwine$quality[x] == "3" | totalwine$quality[x] == "4" | totalwine$quality[x] == "5"){
    totalwine$quality[x] <- "Low"
  }else{
    totalwine$quality[x] <- "Medium"
  }
}

totalwine$quality <- factor(totalwine$quality, ordered = TRUE,levels = c("Low", "Medium", "High"))

```


#Interactive Graph 3 Proportions
```{r}
totalwine %>%
  count(type, quality) %>%
  group_by(type) %>%
  mutate(prop = n / sum(n)) %>%
  plot_ly(x = ~type, y = ~prop, color = ~quality) %>%
  add_bars(opacity = 0.5) %>%
  layout(barmode = "stack")
```

# Interactive Scatter Plot
```{r}

totalwine %>%
  filter(residual.sugar > 15 & residual.sugar < 30 & fixed.acidity > 5.5 & fixed.acidity < 9) %>%
  plot_ly(x = ~residual.sugar, y = ~fixed.acidity, symbol = ~quality ) %>%
  add_markers(marker = list(opacity=0.5, size = 10))
```

# Interactive Bar Chart
```{r}
totalwine %>%
  plot_ly(x = ~quality, y = ~alcohol) %>%
  add_boxplot()
```

# Interactive Graph 

```{r}
wine %>%
  plot_ly(x = ~Flavanoids, y = ~Alcohol, symbol = ~Type, hoverinfo = "text",
          text = ~paste("Flavanoids: ", Flavanoids, "<br>", "Alcohol: ", Alcohol, "<br>", "Phenols: ", Phenols)) %>%
  add_markers(colors = c("orange", "green", "blue"), marker = list(size = 12, opacity = 0.5)) %>%
  layout(xaxis = list(title = "Flavanoids Conc.", type = "log"),
         yaxis = list(title = "Alcohol Percentage"),
         title = "Title Here")
  
```

# Interactive Graph Customize Grid

```{r}

rands <- sample_n(totalwine, 1000)

rands %>%
  plot_ly(x = ~free.sulfur.dioxide, y = ~total.sulfur.dioxide) %>%
  add_markers(marker = list(opacity = 0.5)) %>%
  layout(xaxis = list(title = "Free SO2 (ppm)", showgrid = FALSE),
         yaxis = list(title = "Total SO2 (ppm)"),
         paper_bgcolor = toRGB("grey90"),
         plot_bgcolor = toRGB("pink"))
```

# Adding Layers (Smoother)

```{r}
m <- loess(total.sulfur.dioxide ~ free.sulfur.dioxide, data = rands, span = 1.5)
pol <- lm(total.sulfur.dioxide ~ poly(free.sulfur.dioxide, 2), data = rands)

rands %>%
  plot_ly(x = ~free.sulfur.dioxide, y = ~total.sulfur.dioxide) %>%
  add_markers(showlegend = FALSE) %>%
  add_lines(y = ~fitted(pol), name = "Polynomial") %>%
  add_lines(y = ~fitted(m), name = "LOESS")
  
```

# Density Layering

```{r}
d1 <- filter(rands, type == "white")
d2 <- filter(rands, type == "red")

density1 <- density(d1$citric.acid)
density2 <- density(d2$citric.acid)

plot_ly(opacity = 0.5) %>%
  add_lines(x = ~density1$x, y = ~density1$y, name = "white", fill = 'tozeroy') %>%
  add_lines(x = ~density2$x, y = ~density2$y, name = "red", fill = 'tozeroy') %>%
  layout(xaxis = list(title = 'Citric.acid', showgrid = FALSE),
         yaxis = list(title = 'Density'))
```

# Subplots

```{r}
p1 <- wine %>%
  filter(Type == c(3)) %>%
  plot_ly(x = ~Alcohol, y = ~Malic) %>%
  add_markers(name = ~Type)

p2 <- wine %>%
  filter(Type == c(1,2)) %>%
  plot_ly(x = ~Alcohol, y = ~Malic) %>%
  add_markers(name = ~Type)

subplot(p1, p2, nrows = 1, shareY = TRUE, shareX = TRUE)
```

# Subplots Correct

```{r}
cardata <- mtcars
cardata$cyl <- factor(cardata$cyl)

cardata %>%
  group_by(cyl) %>%
  do(
    plot = plot_ly(data = ., x = ~mpg, y = ~hp) %>%
       add_markers(name = ~carb) %>%
      subplot(nrows = 2)
    )
```


# Binned Scatterplot

```{r}
totalwine %>%
  plot_ly(x = ~residual.sugar, y = ~alcohol) %>%
  add_histogram2d(nbinsx = 100, nbinsy = 50)
```

# Election Data
```{r}
turnout <- read.csv("turnout.txt", header = TRUE, sep = ",")

str(turnout)
```

```{r}
turnout %>%
plot_geo(locationmode = 'USA-states') %>%
  add_trace(
    z = ~turnout,
    locations = ~state.abbr
  ) %>%
  layout(geo = list(scope = 'usa'))
```


# Interactive 3D graph
```{r, echo = FALSE}
kd = with(MASS::geyser, MASS::kde2d(duration, waiting, n =50))
p = plot_ly(x = kd$x, y = kd$y, z = kd$z) %>% add_surface()
p
```
# Interactive Bar Graph
```{r, echo = FALSE}


popdata = population[population$population > 200000000,]

p <- plot_ly(popdata, x = ~population, color = ~country, type = "box")

p
```











